\newpage
\section{Assigned Reading Question [4 points]}
Please read the Quanta article \emph{Computation Is All Around Us, and You Can See It if You Try}, by Lance Fortnow.  The article is available at the link below:
\begin{center}
{\small\href{https://www.quantamagazine.org/computation-is-all-around-us-and-you-can-see-it-if-you-try-20240612/}{https://www.quantamagazine.org/computation-is-all-around-us-and-you-can-see-it-if-you-try-20240612/}}
\end{center}
After reading this article, please answer the question below.

\medskip

\noindent\underline{Question:}
Does Lance Fortnow believe that randomness is unpredictable?  Justify your answer.

\medskip

Lance Fortnow does not believe that randomness is unpredictable. Instead, he believes 
that randomness is processes that are incomprehensible to us. The initial example he gave 
was flipping a coin. We view flipping a coin as a random 50/50 event, however the result 
of flipping that coin is governed by variables like air resistance, the initial force of 
the flip, the mass of the coin, the angle of the toss, etc. These factors influence the 
result of the flip, and a slight change to any could change the outcome of the flip. 
There are too many factors for a human to be able to calculate whether a coin toss would 
be heads or tails, but a being with enough intellect might be. Fortnow believes that all 
random events are not random and can be predicted by computations. He then talks about 
machine learning models and if they keep progressing at their current rate, in a few 
decades they might be able to predict random events.
